---
title: "PSU Data Science"
author: "Bill Stein"
date: "August 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "../")
knitr::opts_chunk$set(echo = TRUE)
```

## Bike Counts on Portland Bridges

In PSU's Data Science class for August 2018, we were supplied a dataset of daily bicycle counts on select bridges across the Willamette River in Portland, Oregon. 

```{r table1, echo=FALSE, message=FALSE}
source("table1.R")

outpu_df
```

The counts were distributed as viewed in this graph.

```{r plot1, echo=FALSE, message=FALSE}
source("plot1.R")

count_plot
```

We proved in class that bicycle use is highest when a day's minimum temperature is between freezing and 65F.

```{r plot2, echo=FALSE, message=FALSE}
source("plot2.R")

tmin_plot
```

I started to test whether there's also a relationship between bike counts and a day's minutes of sunlight. I plan to complete this test outside of class. Here's a snapshot of the data.

```{r table2, echo=FALSE, message=FALSE}
source("table2.R")

sunlight[1:10,]
```
